Blog post: Smart quotes, em dashes, and en dashes

### 2020-07-23 text/20/ihme-covid-model.Rmd
Fixed multiple tags, part 9

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
category: Blog post
tags: Epidemiology
output: html_document
---

@@

You will never resolve the controversy over theoretical versus atheoretical models, but in infectious disease modeling, the theoretical models have several important advantages. 
First, the SEIR models are battle-hardened. They have been used successfully many times in the past. Every year a new flu season offers a new test of these models and every year they seem to do reasonably well.

@@

Begley S. Influential Covid-19 model uses flawed methods and shouldn’t guide U.S. policies, critics say. Stat 2020-04-17. Available in [html format](https://www.statnews.com/2020/04/17/influential-covid-19-model-uses-flawed-methods-shouldnt-guide-policies-critics-say/).

@@

Chowell G, Sattenspiel L, Bansal S, Viboud C. Mathematical models to characterize early epidemic growth: A review. Phys Life Rev. 2016;18:66–97. doi:10.1016/j.plrev.2016.07.005. Available in [html format](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5348083/) or [pdf format](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5348083/pdf/nihms-802148.pdf).

>>>>

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

@@

You will never resolve the controversy over theoretical versus atheoretical models, but in infectious disease modeling, the theoretical models have several important advantages.

First, the SEIR models are battle-hardened. They have been used successfully many times in the past. Every year a new flu season offers a new test of these models and every year they seem to do reasonably well.

@@

Begley S. Influential Covid-19 model uses flawed methods and shouldn?t guide U.S. policies, critics say. Stat 2020-04-17. Available in [html format](https://www.statnews.com/2020/04/17/influential-covid-19-model-uses-flawed-methods-shouldnt-guide-policies-critics-say/).

@@

Chowell G, Sattenspiel L, Bansal S, Viboud C. Mathematical models to characterize early epidemic growth: A review. Phys Life Rev. 2016;18:66?97. doi:10.1016/j.plrev.2016.07.005. Available in [html format](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5348083/) or [pdf format](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5348083/pdf/nihms-802148.pdf).

### 2020-07-23 text/20/map-projections.Rmd
Fixed multiple tags, part 9

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
category: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2020-07-23 text/20/misuse-of-gradient.Rmd
Fixed multiple tags, part 9

---
title: "Blog post: An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
category: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Blog post: An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2020-07-23 text/20/non-breaking-space.Rmd
Fixed multiple tags, part 9

---
title: "Blog post: Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
category: Blog post
tags: Data management
output: html_document
---

@@

```{r insert}
tst1 <- " "
tst1
```

>>>>

---
title: "Blog post: Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: "New"
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
---

@@

```{r insert}
tst1 <- "?"
tst1
```

### 2020-07-23 text/20/smart-quotes.Rmd
Fixed multiple tags, part 9

---
title: "Blog post: Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
category: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Blog post: Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---
